---
title: Social status in mouse social hierarchy is associated with oxytocin and vasopressin
  1a receptor density
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

Run "all_analysis.R" first to display results/figures

## 1. Social hierarchies
### Observation hours/days
```{r}
# number of days of observation
day
day%>%summary()

# number of observation hours
hours
hours%>%
  ungroup() %>%
  .$totalobs %>%
  sum

#total contests
alldata %>% 
  filter(Actor!="Start" & Actor!="End") %>%
  nrow()

#total hours PER day
alldata %>%
  filter(Actor=="End") %>% 
  group_by(cohort) %>% 
  top_n(1,uniqueobs) %>% 
  as.data.frame() %>%
  summarise(ave_total_obs_hour=mean(uniqueobs/day))
```

### Landau's h, Triangle transitivity
```{r}
summary(unlist(sapply(cohort_devries, "[", 1)))
unlist(sapply(cohort_devries, "[", 2))

summary(unlist(sapply(cohort_ttritest, "[", 2)))
unlist(sapply(cohort_ttritest, "[", 3))

summary(unlist(sapply(cohort_dctest, "[", 7)))
unlist(sapply(cohort_dctest, "[", 1))
```

### Despotism
```{r}
summary(despot$despotism)
```

### Glicko plot
```{r, echo=F, fig.width=8,fig.height=12}
grid.arrange(glickoplot[[1]],glickoplot[[2]],glickoplot[[3]],glickoplot[[4]],
             glickoplot[[5]],glickoplot[[6]],glickoplot[[7]],glickoplot[[8]],nrow=4)
```

### body weight ~ rank
Spearman's rank test then corrected for multiple comparison 
```{r}
p.adjust(bw.pval,method="BH") #all p>0.68
```


#02. Analysis of OTR and V1aR density 
optical density~social status+(1|cohort)+(1|Film)
```{r}
est[,1:3]
```

### Figure 1.OTR density by social status groups in six brain regions analyzed. 
Figure 1a: representative figures with a label to each brain region
Figure 1b: raw data points & boxplots (with one y axis)
Figure 1c: Bayesian stat result; mean estimate and 95% CI, posterior sentity plots from group comparisons with point range plot right underneath
```{r}
print(fig1b)
print(fig1c)
```

### Figure 2. V1aR density by social status groups in six brain regions analyzed. 
```{r}
print(fig2b)
print(fig2c)
```

